Decorrelating Errors in Quantum Gates by Random Gate Synthesis

### 2018-07-09 decorrelation/decorrelation.tex
some updates

\section{Optimal Control Problem}\label{ocp}
To explore the utility of BCSs, we consider the following Hamiltonian:
\begin{equation}\label{eq:2}
  H(t) = H_0 + \sum_{i=1}^n (c_i(t) + \delta_i(t))H_i
\end{equation}
for control Hamiltonians $H_{i\neq0}$, free evolution Hamiltonian $H_0$ and time-varying random variables $\delta_i$ are random variables. Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time. Correlations between different $\delta_i$ could arise if two of the control have the same noise source, e.g. $X$ and $Y$ gates in superconducting qubit architectures might use the same AWG and pulse envelope.

After using GRAPE to produce a collection of controls, we must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}). To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate. If we consider the Pauli-Liouville representation of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} operations. In particular, we see that we can write a convex sum over these channels as:
\begin{align}
 \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}
\end{align}
Now, to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
\begin{equation}\label{eq:minimization}
  \begin{split}
    &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{i\neq j}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
    &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
    &\textbf{subject to} \sum_{i=1}^Nw_i = 1
  \end{split}
\end{equation}

@@

\section{2Q Gates}\label{2Q Gates}
 In this section, we present numerical results on a generating one and two-qubit gates that together with $RZ(\theta)$ rotations are universal for two-qubit computation. Our control Hamiltonian is given as: 
\begin{equation} \label{eq:2Qham}
H = \sum_{j=1}^2\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j)
\end{equation}
We again assume that the standard deviations are $.001$ on all parameters $\delta_j$ and $c^j_i$ and that errors on the single qubit $\sigma_x$ and $\sigma_y$ rotations are perfectly correlated.
[ADD ANALYSIS OF PLOTS]
%These plots take a little while to make, so I can't iterate *that* fast - clearly the fonts need to be bigger, and there should be a title what else add a legend saying the black is the optimal?
\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{2Q.png}
\caption{In the above we have used our method to produce a BCS for a ZZ($\frac{\pi}{2}$) entangling gate with controls given by \ref{eq:2Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}

>>>>

\section{Optimal Control Problem}\label{ocp}
\subsection{Random Gate Synthesis}
To explore the utility of BCSs, we consider the following Hamiltonian:
\begin{equation}\label{eq:2}
  H(t) = H_0 + \sum_{i=1}^n (c_i(t) + \delta_i(t))H_i
\end{equation}
for control Hamiltonians $H_i$, free evolution Hamiltonian $H_0$ and time-varying random variables $\delta_i$. Such a model might describe a superconducting qubit quantum processor where control amplitudes for the RF pulses vary over time. Correlations between different $\delta_i$ might arise if two of the controls have the same noise source. Examples of shared noise sources include $X$ and $Y$ gates in superconducting qubit architectures might use the same AWG and pulse envelope, and diurnal temperature drift of control electronics.
\subsection{Channel Approximation}
After using GRAPE or another optimal control routine to synthesize a collection of controls, we must find the weights $w_i$ such that the collection of controls form a BCS as described in (\ref{eq:1}). To do this, for each control $U_i$ we find the unitary error channel $\mathcal{E}_i$ such that $\mathcal{E}_iU_i=U_T$, where $U_T$ is the target gate. If we consider the Pauli-Liouville representation of this error channel, the diagonal terms are the \textit{stochastic} terms that arise from classical uncertainty, while the off-diagonal terms may more generally arise from \textit{coherent} operations. In particular, we see that we can write a convex sum over these channels as:
\begin{align}
 \frac{1}{N} \sum^N_{i=1} w_i \mathcal{E}^{\dagger} (U_T\rho U_T^{\dagger}) \mathcal{E}
\end{align}
Now, to approximate a depolarizing channel we define our optimal control problem to be the following, which minimizes the off-diagonal terms:
\begin{equation}\label{eq:minimization}
  \begin{split}
    &\underset{w_0, ..., w_N}{\textbf{minimize}} \{\sum_{i\neq j}^N|\sigma_i\Lambda(\sigma_j)|^2\}\\
    &\textbf{where}\ \Lambda(\sigma_j) := \sum^N_{i=1}w_i\mathcal{E}_i^{\dagger}\sigma_j\mathcal{E}_i\\
    &\textbf{subject to} \sum_{i=1}^Nw_i = 1
  \end{split}
\end{equation}

@@

\section{2Q Gates}\label{2Q Gates}
 In this section, we present numerical results on a generating one and two-qubit gates that together with $RZ(\theta)$ rotations are universal for two-qubit computation. Our control Hamiltonian is given as: 
\begin{equation} \label{eq:2Qham}
H = \exp{(-i\frac{\sigma_z^1\otimes\sigma_z^2}{4})} + \sum_{j=1}^2(\epsilon_j\sigma_z^j + (1 + \delta_j)(c_x^jx(t)\sigma_x^j + c_y^j(t)\sigma_y^j))
\end{equation}
We again assume that the standard deviations are $.001$ on all parameters $\delta_j$ and $c^j_i$ and that errors on the single qubit $\sigma_x$ and $\sigma_y$ rotations are perfectly correlated.
[ADD ANALYSIS OF PLOTS]
%These plots take a little while to make, so I can't iterate *that* fast - clearly the fonts need to be bigger, and there should be a title what else add a legend saying the black is the optimal?
\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{2Q.png}
\caption{In the above we have used our method to produce a BCS for a ZZ($\frac{\pi}{2}$) entangling gate with controls given by \ref{eq:2Qham}. A) shows the sum of the squared norms of the off diagonal terms in the Pauli Transfer Matrix of $\mathcal{E}$. B) gives the corresponding infidelity for each member of the BCS, and the optimal choice of weights.}
\end{figure*}
